\begin{acknowledgments}
  This thesis and the associated modeling project 
  would not have been possible without the support of many people. 
  Specifically, I would like to thank my advisor, Dr.~Margaret Mathison,
  for her unceasing encouragement, advice, and belief in my capabilities 
  (even at times when I did not fully believe in them myself). 
  Her technical knowledge in the subject area was a 
  great asset to the project, to be sure.
  But of equal or greater importance to me was 
  her constant patience and willingness to provide advice, 
  keeping me grounded through this entire process.
  
  I would also like to thank the other members of my committee:
  Dr.~Anthony Bowman provided valuable advice on EES features,
  helped me through my first experiences as a teaching assistant, 
  and took time to give me a tour of the department when I was 
  first considering Marquette for graduate school.
  Mr.~John Trevino, Jr.~served as my main technical contact at JCI
  for the project. I thank him for taking time to answer my questions
  or pointing me towards people with the answers, hosting and helping
  me during my trip to York during November 2012, and for providing
  valuable feedback on the usability of the model in everyday work.
  Finally, I thank Dr.~Robert Turney for serving as my mentor
  during my internship at JCI, showing me the benefits of model-based
  design processes and automated testing approaches, and continuing
  his commitment to my education through serving on my committee.
  
  While not formally members of my committee, two more 
  engineers merit special recognition here. 
  I would like to acknowledge Mr.~Brett Lenhardt and Mr.~Steven Sommer.
  Mr.~Lenhardt's dynamic modeling work at JCI inspired my interest
  in modeling specifically applied to thermal and fluid systems.
  He also provided feedback as the project was defined and progressed.
  Mr.~Sommer provided valuable comments on my thesis as well as crucial
  insight during project meetings. He also facilitated my November 2012 trip
  to York, PA, during which I learned about the equipment modeled here
  and collected experimental data essential to the validation of the model.

  Special thanks to the faculty and staff in the Department of 
  Mechanical Engineering, the Graduate School, and Marquette University 
  as a whole for their funding through my teaching assistantship and other support.
  Your efforts and support made my graduate school education possible.
  To my students: your dedication and perseverance 
  inspired me during my time at Marquette. 
  I would also like to acknowledge my fianc\'ee, Elise, 
  my parents, Timothy and Shelley, and the rest of my family for their 
  never-ending support, encouragement, understanding, and love.

  \vfill \centering
    \emph{Soli Deo gloria.}
  \vfill
\end{acknowledgments}
